The Multi-Stencil Framework: A Component-Based Approach to Orchestrate Stencils

### 2017-03-06 ARTICLES/IJPP/articleR1/parallelism.tex
corrections related + conclusion
corrections

\begin{figure}[h!]
\begin{center}
\subfloat[Over-constraint on the forbidden $N$ shape.\label{fig:over}]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (c0) at (0,0) {$k_0$};
   \node[] (bc0) at (-1,0) {};
   \node[] (c1) at (2,0) {$k_1$};
   \node[] (c2) at (0,-1) {$k_2$};
   \node[] (bc2) at (-1,-1) {};
   \node[] (c3) at (2,-1) {$k_3$};

  \path[->]
    (bc0) edge [dotted] node {} (c0)
    (bc2) edge [dotted] node {} (c2)
    (c0) edge node {} (c1)
          edge [dashed] node [swap] {} (c3)
    (c2) edge node {} (c1)
        edge node {} (c3);
  \end{tikzpicture}
}
\hspace{30pt}
\subfloat[TSP tree of Fig.~\ref{fig:over}\label{fig:solu}]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (S0) at (0,0) {$\mathcal{S}$};
   \node[] (bS0) at (-1,-1) {};
   \node[] (P1) at (-1,1) {$\mathcal{P}$};
   \node[] (aP1) at (-1.5,2) {$k_0$};
   \node[] (aaP1) at (-0.5,2) {$k_2$};
   \node[] (P2) at (1,1) {$\mathcal{P}$};
   \node[] (c1) at (0.5,2) {$k_1$};
   \node[] (c3) at (1.5,2) {$k_3$};

  \path[->]
    (bS0) edge [dotted] node {} (S0)
    (S0) edge node {} (P1)
         edge node {} (P2)
    (P1) edge node [swap] {} (aP1)
          edge node [swap] {} (aaP1)
    (P2) edge node {} (c1)
        edge node {} (c3);
  \end{tikzpicture}
}
\label{fid:nshape}
\caption{N-Shape problem and solution}
\end{center}
\end{figure}

@@

As a result, the critical point for performance is when $T_{COM} \geq \frac{T_{SEQ}}{P}$, which happens naturally in data parallelization as $T_{COM}$ will increase with the number of processes, and $\frac{T_{SEQ}}{P}$ decrease with the number of processes.
\JB{Pour moi $T_{COM}$ est constant quand on communique entre voisins... Il diminue meme legerement si on reduit les donnees par process.}

>>>>

\begin{figure}[t]
\begin{minipage}{.475\textwidth}
\begin{center}
  \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (c0) at (0,0) {$k_0$};
   \node[] (bc0) at (-1,0) {};
   \node[] (c1) at (2,0) {$k_1$};
   \node[] (c2) at (0,-1) {$k_2$};
   \node[] (bc2) at (-1,-1) {};
   \node[] (c3) at (2,-1) {$k_3$};

  \path[->]
    (bc0) edge [dotted] node {} (c0)
    (bc2) edge [dotted] node {} (c2)
    (c0) edge node {} (c1)
          edge [dashed] node [swap] {} (c3)
    (c2) edge node {} (c1)
        edge node {} (c3);
  \end{tikzpicture}
  \caption{Over-constraint on the forbidden $N$ shape.}
  \label{fig:over}
 \end{center}
\end{minipage}
\hfill
\begin{minipage}{.475\textwidth}
\begin{center}
  \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (S0) at (0,0) {$\mathcal{S}$};
   \node[] (bS0) at (-1,-1) {};
   \node[] (P1) at (-1,1) {$\mathcal{P}$};
   \node[] (aP1) at (-1.5,2) {$k_0$};
   \node[] (aaP1) at (-0.5,2) {$k_2$};
   \node[] (P2) at (1,1) {$\mathcal{P}$};
   \node[] (c1) at (0.5,2) {$k_1$};
   \node[] (c3) at (1.5,2) {$k_3$};

  \path[->]
    (bS0) edge [dotted] node {} (S0)
    (S0) edge node {} (P1)
         edge node {} (P2)
    (P1) edge node [swap] {} (aP1)
          edge node [swap] {} (aaP1)
    (P2) edge node {} (c1)
        edge node {} (c3);
  \end{tikzpicture}
  \caption{TSP tree of Fig.~\ref{fig:over}.}
  \label{fig:solu}
 \end{center}
\end{minipage}\end{figure}

%\begin{figure}[h!]
%\begin{center}
%\subfloat[Over-constraint on the forbidden $N$ shape.\label{fig:over}]{
%\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%   \node[] (c0) at (0,0) {$k_0$};
%   \node[] (bc0) at (-1,0) {};
%   \node[] (c1) at (2,0) {$k_1$};
%   \node[] (c2) at (0,-1) {$k_2$};
%   \node[] (bc2) at (-1,-1) {};
%   \node[] (c3) at (2,-1) {$k_3$};
% 
%  \path[->]
%    (bc0) edge [dotted] node {} (c0)
%    (bc2) edge [dotted] node {} (c2)
%    (c0) edge node {} (c1)
%          edge [dashed] node [swap] {} (c3)
%    (c2) edge node {} (c1)
%        edge node {} (c3);
%  \end{tikzpicture}
%}
%\hspace{30pt}
%\subfloat[TSP tree of Fig.~\ref{fig:over}\label{fig:solu}]{
%\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%   \node[] (S0) at (0,0) {$\mathcal{S}$};
%   \node[] (bS0) at (-1,-1) {};
%   \node[] (P1) at (-1,1) {$\mathcal{P}$};
%   \node[] (aP1) at (-1.5,2) {$k_0$};
%   \node[] (aaP1) at (-0.5,2) {$k_2$};
%   \node[] (P2) at (1,1) {$\mathcal{P}$};
%   \node[] (c1) at (0.5,2) {$k_1$};
%   \node[] (c3) at (1.5,2) {$k_3$};
% 
%  \path[->]
%    (bS0) edge [dotted] node {} (S0)
%    (S0) edge node {} (P1)
%         edge node {} (P2)
%    (P1) edge node [swap] {} (aP1)
%          edge node [swap] {} (aaP1)
%    (P2) edge node {} (c1)
%        edge node {} (c3);
%  \end{tikzpicture}
%}
%\label{fid:nshape}
%\caption{N-Shape problem and solution}
%\end{center}
%\end{figure}

@@

As a result, the critical point for performance is when $T_{COM} \geq \frac{T_{SEQ}}{P}$, which happens naturally in data parallelization as $T_{COM}$ will increase with the number of processes, and $\frac{T_{SEQ}}{P}$ decrease with the number of processes.
%\JB{Pour moi $T_{COM}$ est constant quand on communique entre voisins... Il diminue meme legerement si on reduit les donnees par process.}
